%-------------------------
% Resume in Latex
% Author : Vishal Kathpalia
% Based off of: https://github.com/Er-Vishal-Kathpalia
% Designation: Software Engineer
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Vishal Kathpalia} \\ \vspace{1pt}
    Bangalore, India \\ \vspace{1pt}
    \small \raisebox{-0.2\height}\faPhone\ +917404899901 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{vishalkathpalia99@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/er-vishal-kathpalia/}{\raisebox{-0.2\height}\faLinkedin\ \underline{/vishal-kathpalia}}  ~
    \href{https://github.com/Er-Vishal-Kathpalia}{\raisebox{-0.2\height}\faGithub\ \underline{/vishal-kathpalia}}
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tekion Corp}{ Jul 2022 -- Now}
      {Associate Software Engineer}{Bangalore, Karnataka}
      \resumeItemListStart
        \resumeItem{Actively contributed to the maintenance of 8–9 microservices using Spring, MySQL, MongoDB, Elastic Search, and Kafka to work on and delivered 15 major and minor features.} 
        \resumeItem{ Worked upon writing 3 new microservices from the scratch and changed the architecture of existing workflows of customer communication and printing the PDFs and labels.}
        \resumeItem{Explored the APIs throughput and worked upon making the APIs more efficient and responsive after analysing and taking some of the sync process in async manner. }
      \resumeItemListEnd

    \resumeSubheading
      {Tekion Corp}{Jan 2022 -- Jul 2022}
      {Associate Software Engineer Intern}{Bangalore, Karnataka}
      \resumeItemListStart
        \resumeItem{Explored the design of recruitement portal and worked upon writing the recruitment portal of tekion from backend for talent acquisition team.}
        \resumeItem{Worked upon writing the APIs of tekhire using Spring Framework, Elastic Search and Kafka.}
        \resumeItem{Contributed in writing the migration APIs in batches to migrate the existing data from old greenhouse portal to tekhire portal and made the onboarding smooth for HR team.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lovely Professional University}{Aug 2018 -- May 2022}
      {B.Tech in Computer Science and Engineering}{Phagwara, Punjab}
    \resumeSubheading
      {Swami Vivekanand Public School}{Mar 2003 -- Aug 2018}
      {XII-(CBSE)}{Yamuna Nagar, Haryana}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Skills}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures and Algo
                \item Kafka
                \item Spring Framework
                \item Database Management
                \item Elastic Search
                \item OOPS concepts
                \item Java Programming
                \item MongoDB $\&$ MySql
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{URL Shortener} $|$ \emph{Spring, MongoDB}}{March 2022}
          \resumeItemListStart
            \resumeItem{Developed an application used to generate url shortener using Spring Framework, REST APIs with mongodb database.}
            \resumeItem{Explored the google guava library in gradle to generate the unique hash code and save in the MongoDB database.}
            \resumeItem{Added an privacy feature in the URL shortener so people can share the private link after adding a password.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Speech Recognition Software} $|$ \emph{Python, SpeechRecognition }}{November 2019}
          \resumeItemListStart
            \resumeItem{GUI-based programme that functions similarly like Microsoft Cortana. It has many sections and functions as a computer's assistant. People can control the computer using Speech.}
            \resumeItem{Explored the SpeechRecognition, Pyaudio, and Pyqt5 packages of python to develop this project.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Servo Door Lock System with Keypad and Bluetooth Android App} $|$ \emph{IOT, Arduino UNO}}{February 2019}
          \resumeItemListStart
            \resumeItem{IOT project that can be used for security purpose in which door can be unlock by password using keypad.}
            \resumeItem{Hardware project in which Servo motor, Manual keypad, Arduino UNO, Display, Buzzer, Lights has been used to develop the project and sdded a functionality to control the door lock system using mobile application.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C, C++, Java, Python, R programming} \\
     \textbf{Developer Tools}{: IntelliJ IDEA, Eclipse, Jira, Confluence} \\
     \textbf{Technologies/Frameworks}{: Spring Boot, Linux, Elastic Search, Kafka} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Academics / Extracurricular Achievements}
\vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
        {\textbf{GeeksForGeeks Self Paced Data Structure Course}\emph{}}{DS-Algo}
            \resumeItemListStart
                \resumeItem{Learned Data structures and algorithm concepts using C++ and solved the problems.}
            \resumeItemListEnd
            \vspace{-20pt}
        \resumeProjectHeading
        {\textbf{Won the First Prize In Science Exhibition}\emph{ }}{Science, Physics}
            \resumeItemListStart
                \resumeItem{Build the Tesla Coil project and represents the school in science exhibition.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
